---
title: "Five Parameters"
author: "Aashna"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false
library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
```


```{r}
#| label: plot
fit_all |>
  add_epred_draws(newdata = ndata) |> 
  ggplot(aes(.epred, fill = sex)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 alpha = 0.5,
                 bins = 100,
                 position = "identity") +
  scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  labs(title = "Posterior for expected years lived post-election", 
  subtitle = "Male candidates live longer", 
  x = "Years", y = "Probability")
```
We are using data from deceased U.S. gubernatorial candidates between 1945 and 2012 to forecast post-election longevity. Our goal is to understand how lived_after differs between male and female candidates. Using a Bayesian regression model, we found that the interaction between sex and election age suggests that as election age increases, the life expectancy difference between male and female governors tends to widen. Male candidates are predicted to live longer, with some uncertainty around this estimate.
 
We are using data from deceased U.S. gubernatorial candidates between 1945 and 2012 to forecast candidate longevity in state-wide races post-election. Our goal is to understand how lived_after differs between male and female candidates. A potential problem is the lack of representativeness, as the dataset excludes living candidates and recent elections, potentially biasing our findings.




```{r}
#| label: model
#| cache: true

fit_all <- $$ lived\_after_i =  \beta_0 + \beta_1 male_i + \beta_2 c\_election\_age_i + 
\\ \beta_3 male_i *  c\_election\_age_i + \epsilon_i $$
```


Using data from all deceased gubernatorial candidates in the United States from elections held between 1945 and 2012, we seek to forecast candidate longevity in state-wide US races post-election. There is concern that longevity for gubernatorial candidates will differ significantly from that for candidates in Senate and other state-wide elections. We are using a Bayesian regression model with the formula lived_after ~ sex * election_age to analyze the data, where lived_after is the dependent variable representing post-election life expectancy. The model reveals that the interaction between sex and election age has a positive direction, suggesting that as election age increases, the life expectancy difference between male and female governors tends to widen.







